---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# autheliar

[![Travis build status](https://travis-ci.org/liamgilbey/autheliar.svg?branch=master)](https://travis-ci.org/liamgilbey/autheliar)
[![Codecov test coverage](https://codecov.io/gh/liamgilbey/autheliar/branch/master/graph/badge.svg)](https://codecov.io/gh/liamgilbey/autheliar?branch=master)

The goal of autheliar is to provide an R interface to the Authelia API, allowing 
a low-overhead way to bring authentication into R applications.

## Installation

For now this package is only available from GitHub.

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("liamgilbey/autheliar")
```


## Usage

The central object to `autheliar` is the R6 class `authelia`. As with all R6 classes, a new `ldap` object is created with the `new` method:


```{r, eval = FALSE}
auth <- autheliar::authelia$new("https://authelia.example.com")
```


Logging into the server can be achieved using first-factor authentication:

```{r, eval = FALSE}
auth$firstfactor(
  username = "John",
  password = "secretpassword"
)
```

